PMV: Which formulation should you use the ISO 7730:2005 or ASHRAE 55:2020?

### 2023-09-01 Manuscript/src/sections/results.tex
paper: added reference and fixed sentence

\subsection{Model Bias}\label{sec:model-bias}
\subsubsection{Model Overall Bias}\label{subsec:model-overall-bias}
We calculated the overall bias of the model as previously done by \mycite{Humphreys2002} by subtracting the \ac{pmv} and  \ac{pmv-ce} models prediction from the self-reported \ac{tsv}.
Results are presented in Figure~\ref{fig:hist_discrepancies}.
% todo:
%  You need to check of the four distibution are normally distributed, if so, report mean and SD, if not report median and IQR, no need to report all of them.
%  I guess that Pswetest is an indication of this, so, for the entire dataset it seems that it is not sufficiently normally distributed, so report only median and IQR.
%  The Pswetest This index is not reported, explained, and interpreted in the paper.
%  Can this chart be transformed in a letter value plot?
%  The Caption is missing
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/hist_discrepancies}
    \caption{}
    \label{fig:hist_discrepancies}
\end{figure*} 
Overall both the \ac{pmv} and \ac{pmv-ce} models have a median bias lower than half of a thermal sensation interval.
Figure~\ref{fig:hist_discrepancies} contains the summary statistics, and the results highlight that the \ac{pmv-ce} had a higher bias than the \ac{pmv} when using the entire dataset.
The two models only differ when \ac{v} exceeds \qty{0.1}{\m\per\s}; we also calculated the bias of the model, including data points with \ac{v} higher than \qty{0.2}{\m\per\s} since above this value the differences in the outputs of the two models are more pronounced.
We set the limit to \qty{0.2}{\m\per\s} and not a higher value since, as previously shown in Figure~\ref{fig:dist_input_data}, we could only reliably test the accuracy of the models up to \ac{v} of \var{v_95_perc_max}.
We did not use \qty{0.1}{\m\per\s} as a threshold because the original difference between the two models was \qty{0.2}{\m\per\s}.
The effect of air movement is perceptible only when the airspeed is sufficiently high to disrupt the body's thermal plume (xxx).
The threshold in the standard was reduced to \qty{0.1}{\m\per\s} to simplify the usability and achieve one threshold for all the air speeds.
The results show that the median bias of the \ac{pmv} model reduced to \var{bias_median_pmv_0.2} from \var{bias_median_pmv_0}, meaning that at higher speed the \ac{pmv} model improved.
Surprisingly, we found that the median bias for the \ac{pmv-ce} increased to \var{bias_median_pmv_ce_0.2} from \var{bias_median_pmv_ce_0}.
These are worrying results since the \ac{pmv-ce} model claims to have a higher accuracy at higher values of \ac{v}, but this is not what was found from this data.
As far as we could find, there is no published paper proving a higher accuracy of the \ac{pmv-ce} compared to the \ac{pmv} model. 
The \ac{pmv-ce} has lower accuracy while making the code more complex and computationally intensive to run.

\subsubsection{Model Bias as Function of Four Input Variables}\label{subsec:model-bias-variable}
In the previous section, we presented the overall bias of the two \ac{pmv} formulations.
We then went on to determine how the bias varied as a function of \ac{tdb}, \ac{v}, \ac{met}, and \ac{clo}.
Figure~\ref{fig:dist_input_data} shows the results.
In each sub-figure, we have binned the results into discrete intervals of equal width, and the x-axis tick label is the center value of the interval. 
The width of the violin plot is not proportional to the number of points in that specific bin.
% todo This figure needs a lot of improvements. 1) I would use the letter-value (or boxplot), they may be easier to interpret, provide less info and could be aligned with the first figure (in particular if  The actual density distribution it is not adding much value. 2) The color for PMV and PMV_CE must be the same in the entire paper. 3) The y-label should be moved to the x-label and the y-label should explicit. I would remove the decimal values and show only the five integers -2, -1, 0, 1 and 2. 4) How is possible to have a velocity "centered" at 0? I would remove the red lines. If you want to underline the -0.5 and 0.5 range, then we should use the same strategy also for figure 7. The fact that you change graph time in the paper, it makes more difficult to interpret without adding a substantial amount of value. 
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/bias_models}
    \caption{}
    \label{fig:bias_models}
\end{figure*}
The results depict that the use of the \ac{pmv-ce} model did not improve the bias of the \ac{pmv} results across all four input variables.
On the contrary, the bias of the \ac{pmv-ce} diverged more from 0 as the value of \ac{v} increased.
These results are in agreement with those presented in the previous section and depict that the correction applied by the \ac{pmv-ce} model worsens the results.

>>>>

\subsection{Model Bias}\label{sec:model-bias}
\subsubsection{Model Overall Bias}\label{subsec:model-overall-bias}
We calculated the overall bias of the model as previously done by \mycite{Humphreys2002} by subtracting the \ac{pmv} and  \ac{pmv-ce} models prediction from the self-reported \ac{tsv}.
Results are presented in Figure~\ref{fig:hist_discrepancies}.
% todo:
%  You need to check of the four distibution are normally distributed, if so, report mean and SD, if not report median and IQR, no need to report all of them.
%  I guess that Pswetest is an indication of this, so, for the entire dataset it seems that it is not sufficiently normally distributed, so report only median and IQR.
%  The Pswetest This index is not reported, explained, and interpreted in the paper.
%  Can this chart be transformed in a letter value plot?
%  The Caption is missing
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/hist_discrepancies}
    \caption{}
    \label{fig:hist_discrepancies}
\end{figure*} 
Overall both the \ac{pmv} and \ac{pmv-ce} models have a median bias lower than half of a thermal sensation interval.
Figure~\ref{fig:hist_discrepancies} contains the summary statistics, and the results highlight that the \ac{pmv-ce} had a higher bias than the \ac{pmv} when using the entire dataset.
The two models only differ when \ac{v} exceeds \qty{0.1}{\m\per\s}; we also calculated the bias of the model, including data points with \ac{v} higher than \qty{0.2}{\m\per\s} since above this value the differences in the outputs of the two models are more pronounced.
We set the limit to \qty{0.2}{\m\per\s} and not a higher value since, as previously shown in Figure~\ref{fig:dist_input_data}, we could only reliably test the accuracy of the models up to \ac{v} of \var{v_95_perc_max}.
We did not use \qty{0.1}{\m\per\s} as a threshold because the original difference between the two models was \qty{0.2}{\m\per\s}.
The effect of air movement is perceptible only when the airspeed is sufficiently high to disrupt the body's thermal plume~\cite{zukowska_impact_2012}.
The threshold in the standard was reduced to \qty{0.1}{\m\per\s} to simplify the usability and achieve one threshold for all the air speeds.
The results show that the median bias of the \ac{pmv} model reduced to \var{bias_median_pmv_0.2} from \var{bias_median_pmv_0}, meaning that at higher speed the \ac{pmv} model improved.
Surprisingly, we found that the median bias for the \ac{pmv-ce} increased to \var{bias_median_pmv_ce_0.2} from \var{bias_median_pmv_ce_0}.
These are worrying results since the \ac{pmv-ce} model claims to have a higher accuracy at higher values of \ac{v}, but this is not what was found from this data.
As far as we could find, there is no published paper proving a higher accuracy of the \ac{pmv-ce} compared to the \ac{pmv} model. 
The \ac{pmv-ce} has lower accuracy while making the code more complex and computationally intensive to run.

\subsubsection{Model Bias as Function of Four Input Variables}\label{subsec:model-bias-variable}
In the previous section, we presented the overall bias of the two \ac{pmv} formulations.
We then went on to determine how the bias varied as a function of \ac{tdb}, \ac{v}, \ac{met}, and \ac{clo}.
Figure~\ref{fig:dist_input_data} shows the results.
In each sub-figure, we have binned the results into discrete intervals of equal width, and the x-axis tick label is the center value of the interval.
All the violin plots have the same area to aid visualization, despite the fact that the number of points in each bin is not constant.
% todo This figure needs a lot of improvements. 1) I would use the letter-value (or boxplot), they may be easier to interpret, provide less info and could be aligned with the first figure (in particular if  The actual density distribution it is not adding much value. 2) The color for PMV and PMV_CE must be the same in the entire paper. 3) The y-label should be moved to the x-label and the y-label should explicit. I would remove the decimal values and show only the five integers -2, -1, 0, 1 and 2. 4) How is possible to have a velocity "centered" at 0? I would remove the red lines. If you want to underline the -0.5 and 0.5 range, then we should use the same strategy also for figure 7. The fact that you change graph time in the paper, it makes more difficult to interpret without adding a substantial amount of value. 
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/bias_models}
    \caption{}
    \label{fig:bias_models}
\end{figure*}
The results depict that the use of the \ac{pmv-ce} model did not improve the bias of the \ac{pmv} results across all four input variables.
On the contrary, the bias of the \ac{pmv-ce} diverged more from 0 as the value of \ac{v} increased.
These results are in agreement with those presented in the previous section and depict that the correction applied by the \ac{pmv-ce} model worsens the results.
